Security vs. Maintainability: \\ Fixing Vulnerabilities Obfuscates your Code

### 2019-01-30 paper/ICPC19/icpc19.tex
removing abstract folder, adding it to the paper

\begin{abstract}
  Security is a crucial non-functionality requirement for software applications.
  However, building secure software is far from trivial as developers lack both
  the knowledge and tools to effectively address this concern. In this paper, we
  study the impact of changes to improve security on the maintainability of several
  open source applications. Using a dataset containing 607 security-oriented
  commits, we measure maintainability --- as computed by the Software Improvement
  Group's web-based source code analysis service \emph{Better Code Hub} (BCH) ---
  before and after the security refactoring. Results show that making software
  more secure comes at a cost on maintainability. This is particularly evident
  in refactorings to deal with \emph{Broken Authentication and Session Management}, 
  \emph{Denial-of-Service} attacks and \emph{Memory Leaks}.
\end{abstract}

@@

@@

\begin{figure}[h]
 	\centering 	\includegraphics[width=0.45\textwidth]{figures/bch_report.png}
 	\caption{Maintainability report of OpenSSL CVE-2014-3506 vulnerability
refactoring for the guideline \emph{Write Simple Units of Code} provided by
\emph{Better Code Hub}. This version of OpenSSL does not comply with the
guideline in the example since the bars do not reach the threshold points. This
example only complies with $\sfrac{1}{10}$ guidelines (\emph{Write Clean Code}).}
	\label{fig:bchrep}
\end{figure}

>>>>

\begin{abstract}
Nowadays, security is an absolutely necessary requirement for the production of quality software. However, there is still a considerable amount of zero-day vulnerabilities published and fixed almost every week. The authors suspect that when developers address these vulnerabilities on their codebases, they actually affect the maintainability of software and even introduce more vulnerabilities. This paper evaluates the impact of refactorings to improve security on the maintainability of open-source software. Maintainability is measured based on the \emph{Better Code Hub}'s model of 10 guidelines for both before and after security commits for a dataset including 607 security commits. Results show that fixing software vulnerabilities harms the maintainability of open-source software. Specially for refactorings that deal with \emph{Broken Authentication and Session Management}, \emph{Memory Leaks} and \emph{Denial-of-Service} attacks. Therefore, it is necessary to bring awareness for coding good practices and for the use of automated tools that have the potential to help developers with this issue.
\end{abstract}

@@

% Our empirical study finds evidence that energy efficiency- oriented code changes have a negative impact on code main- tainability. In particular, careful thinking is required to im- plement the energy patterns Power Save Mode and Wakelock Addition. Furthermore, we show that energy patterns are more likely to require maintenance than regular code changes.

@@

\begin{figure}[]
 	\centering 	\includegraphics[width=0.45\textwidth]{figures/bch_report.png}
 	\caption{Maintainability report of OpenSSL CVE-2014-3506 vulnerability
refactoring for the guideline \emph{Write Simple Units of Code} provided by
\emph{Better Code Hub}. This version of OpenSSL does not comply with the
guideline in the example since the bars do not reach the threshold points. This
example only complies with $\sfrac{1}{10}$ guidelines (\emph{Write Clean Code}).}
	\label{fig:bchrep}
\end{figure}
